Explore tumor cell classification with CellAssign

### 2024-05-28 analyses/cell-type-ewings/template_notebooks/02-cellassign.Rmd
set eval based on existing annotations

---
title: "Explore tumor cell classification with CellAssign"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "../results/annotate_tumor_cells_output/SCPCS000490/SCPCL000822_tumor-normal-classifications.tsv"
  tumor_marker_predictions: "../results/annotate_tumor_cells_output/SCPCS000490/cellassign/SCPCL000822_tumor-only-predictions.tsv"
  visser_marker_predictions: "../results/annotate_tumor_cells_output/SCPCS000490/cellassign/SCPCL000822_visser-predictions.tsv"
  panglao_predictions: "../results/annotate_tumor_cells_output/SCPCS000490/cellassign/SCPCL000822_panglao-predictions.tsv"
  results_dir: "../results/annotate_tumor_cells_output/SCPCS000490"
---

@@

```{r}
# first rename column to combine with cell type df 
visser_celltype_assignments <- visser_celltype_assignments |> 
  dplyr::rename(visser_cellassign_annotations = celltype)

@@

```{r}
# get jaccard similarity index 
jaccard_mtx <- make_jaccard_matrix(celltype_df, "visser_cellassign_annotations", "marker_gene_classification")

@@

```{r}
# first make sure cells have been classified as endothelial 
has_endothelial <- "Endothelial cells" %in% unique(celltype_df$cellassign_celltype_annotation) &&
  "endothelial cells" %in% unique(celltype_df$visser_cellassign_annotations)

@@

```{r}
# get all markers 
all_markers <- visser_markers_df |> 
  dplyr::pull(ensembl_gene_id)

@@

```{r}
# get a list of all celltypes in the reference
celltypes <- unique(visser_markers_df$cell_type)

@@

```{r}
grouped_celltype_df <- marker_gene_exp_df |> 
  # group by barcode and cell type to get the sum 
  dplyr::group_by(barcodes, cell_type) |> 
  dplyr::mutate(mean_exp = mean(gene_expression))

@@

```{r}
# first rename column to combine with cell type df 
panglao_celltype_assignments <- panglao_celltype_assignments |> 
  dplyr::rename(panglao_cellassign_annotations = celltype)

@@

```{r}
# get jaccard similarity index 
jaccard_mtx <- make_jaccard_matrix(celltype_df, "cellassign_celltype_annotation", "panglao_cellassign_annotations")

>>>>

---
title: "Explore tumor cell classification with CellAssign"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "../results/sim_annotate_tumor/SCPCS000490/SCPCL000822_tumor-normal-classifications.tsv"
  tumor_marker_predictions: "../results/sim_annotate_tumor/SCPCS000490/cellassign/SCPCL000822_tumor-marker_predictions.tsv"
  visser_marker_predictions: "../results/sim_annotate_tumor/SCPCS000490/cellassign/SCPCL000822_visser-all-marker_predictions.tsv"
  panglao_predictions: "../results/sim_annotate_tumor/SCPCS000490/cellassign/SCPCL000822_panglao-endo-fibro_predictions.tsv"
  results_dir: "../results/sim_annotate_tumor/SCPCS000490"
---

@@

```{r, eval=has_visser_assignments}
# first rename column to combine with cell type df 
visser_celltype_assignments <- visser_celltype_assignments |> 
  dplyr::rename(visser_cellassign_annotations = celltype)

@@

```{r, eval=has_visser_assignments}
# get jaccard similarity index 
jaccard_mtx <- make_jaccard_matrix(celltype_df, "visser_cellassign_annotations", "marker_gene_classification")

@@

```{r, eval=has_visser_assignments}
# first make sure cells have been classified as endothelial 
has_endothelial <- "Endothelial cells" %in% unique(celltype_df$cellassign_celltype_annotation) &&
  "endothelial cells" %in% unique(celltype_df$visser_cellassign_annotations)

@@

```{r, eval=has_visser_assignments}
# get all markers 
all_markers <- visser_markers_df |> 
  dplyr::pull(ensembl_gene_id)

@@

```{r, eval=has_visser_assignments}
# get a list of all celltypes in the reference
celltypes <- unique(visser_markers_df$cell_type)

@@

```{r, eval=has_visser_assignments}
grouped_celltype_df <- marker_gene_exp_df |> 
  # group by barcode and cell type to get the sum 
  dplyr::group_by(barcodes, cell_type) |> 
  dplyr::mutate(mean_exp = mean(gene_expression))

@@

```{r, eval=has_panglao_assignments}
# first rename column to combine with cell type df 
panglao_celltype_assignments <- panglao_celltype_assignments |> 
  dplyr::rename(panglao_cellassign_annotations = celltype)

@@

```{r, eval=has_panglao_assignments}
# get jaccard similarity index 
jaccard_mtx <- make_jaccard_matrix(celltype_df, "cellassign_celltype_annotation", "panglao_cellassign_annotations")
